### 2017-01-05 local-capability-machine.tex
Changed the definition of worlds

\declaretheorem[numbered=yes,name=Lemma,qed=$\blacksquare$]{lemma}
\declaretheorem[numbered=yes,name=Definition,qed=$\blacksquare$]{definition}
\declaretheorem[numbered=yes,name=Specification,qed=$\blacksquare$]{specification}

@@

% World operations
\newcommand{\future}{\mathbin{\sqsupseteq}}
\newcommand{\futurewk}{\mathbin{\sqsupseteq}^{\var{pub}}}
\newcommand{\futurestr}{\mathbin{\sqsupseteq}^{\var{priv}}}
\newcommand{\heapSat}[3][\heap]{#1 :_{#2} #3}
\newcommand{\memSat}[3][n]{\heapSat[#2]{#1}{#3}}
\newcommand{\memSatPar}[4][n]{\heapSat[#2]{#1 , #4}{#3}}

@@

\newcommand{\Rel}{\plaindom{Rel}}
\newcommand{\States}{\plaindom{State}}
\newcommand{\RegionNames}{\plaindom{RegionName}}
\newcommand{\Regions}{\plaindom{Region}}
\newcommand{\Reg}{\plaindom{Reg}}
\newcommand{\Worlds}{\plaindom{World}}
\newcommand{\Wor}{\plaindom{Wor}}
\newcommand{\Worwk}{\Wor_{\futurewk}}
\newcommand{\Worstr}{\Wor_{\futurestr}}
\newcommand{\xiwk}{\xi_{\var{wk}}}
\newcommand{\xistr}{\xi_{\var{str}}}
\newcommand{\StorePred}{\plaindom{MemSegPred}}
\newcommand{\UPred}[1]{\plaindom{UPred}(#1)}
\newcommand{\DCPred}[1]{\plaindom{P}^\downarrow(#1)}

@@

    c_{\var{adv}} & \defeq ((\entry,\glob),\start_{\adv},\addrend_{\adv},\start_{\adv}+\olf) \\

@@

@@

  \item $\hs_\adv$ contains a read-write capability for $\hs_\link$ on its first address and otherwise it consists only of instruction.

@@

@@

        & [3 \mapsto \iota^\pwl]\\

@@

  and use the FTLR on $c_\adv$ (possible due to lemma~\ref{lem:nwlp-subset-pwl} and the chose world). From this, we get

@@

\section{Logical Relation'}
\subsection{Worlds}
Assume $\Worstr$ and $\Worwk$ are preordered \cofes{} and $\xi_{\var{wk}}$ and $\xi_{\var{str}}$ are isomorphisms such that
\begin{align*}
  \xi_{\var{wk}} :   \Worwk \cong \blater (\nats \finparfun (   & \{\revoked\} + \\
                                                                & \{\temp\} \times \States \times \Rel \times (\States \fun (\Worwk \monnefun \UPred{\HeapSegments})) + \\
                                                                & \{\perma\} \times \States \times \Rel \times (\States \fun (\Worstr \monnefun \UPred{\HeapSegments})))_{\future_{\var{wk}}}) \\ \\
  \xi_{\var{str}} :   \Worstr \cong \blater (\nats \finparfun ( & \{\revoked\} + \\
                                                                & \{\temp\} \times \States \times \Rel \times (\States \fun (\Worwk \monnefun \UPred{\HeapSegments})) + \\
                                                                & \{\perma\} \times \States \times \Rel \times (\States \fun (\Worstr \monnefun \UPred{\HeapSegments})))_{\future_{\var{str}}})
\end{align*}
We now define the regions to be
\begin{align*}
  \Regions = & \{\revoked\} \uplus \\
             & \{\temp\} \times \States \times \Rel \times (\States \fun (\Worwk \monnefun \UPred{\HeapSegments})) \uplus \\
             & \{\perma\} \times \States \times \Rel \times (\States \fun (\Worstr \monnefun \UPred{\HeapSegments}))
\end{align*}
And the worlds are
\[
  \Worlds = \RegionNames \finparfun \Regions
\]
Where $\RegionNames = \nats$.

@@

Standard regions for when writing locally is permitted:
\begin{align*}
  &\iota_{\start,\addrend}^\pwl : \Regions\\
  &\iota_{\start,\addrend}^\pwl \defeq (\temp,1,=,H^\pwl_{\start,\addrend}) \\
  \\
  &H^\pwl : \Addrs^2 \fun \States \fun (\Worwk \monnefun \UPred{\HeapSegments})\\
  &H^\pwl_{\start,\addrend}\; s \; \hat{W} \defeq \left\{\npair{\hs} \middle|
    \begin{aligned}
      &\dom(\hs) = [\start,\addrend] \land \\
      &\forall \addr \in [\start,\addrend] \ldotp \npair[n-1]{\hs(\addr)} \in \stdvr(\xi_{\var{wk}}(\hat{W}))
    \end{aligned}
        \right\}
\end{align*}
\lau{What is the reason to have the ``view'' always be $\temp$? It seems like it does not play well with the read condition if it is always $\temp$.}
Revoking all temporary regions:
\begin{align*}
  \revokeTemp{} & : \Worlds \fun \Worlds \\
  \revokeTemp{W} & \defeq \lambda r \ldotp 
                   \begin{cases}
                     \revoked            & \text{if }W(r) = (\temp,s,\phi,H) \\
                     W(r)                & \text{otherwise}
                   \end{cases}
\end{align*}
\newcommand{\wrev}[1]{\revokeTemp{#1}}

Standard regions for when write local is not allowed:
\begin{align*}
  &\iota_{\start,\addrend}^{\nwl} : \Regions \\
  &\iota_{\start,\addrend}^{\nwl} \defeq (\temp,1,=,H^\nwl_{start,\addrend}) \\
  \\
  &\iota_{\start,\addrend}^{\nwl,p} : \Regions \\
  &\iota_{\start,\addrend}^{\nwl,p} \defeq (\perma,1,=,H^\nwl_{start,\addrend})\\
  \\
  &H^\nwl : \Addrs^2 \fun \States \fun (\Worstr \monnefun \UPred{\HeapSegments})\\
  &H^\nwl_{\start,\addrend} \; s \;\hat{W} \defeq \left\{\npair{\hs} \middle|
    \begin{aligned}
      &\dom(\hs) = [\start,\addrend] \land \\
      &\forall \addr \in [\start,\addrend] \ldotp \\
      &\quad \npair[n-1]{\hs(\addr)} \in \stdvr(\revokeTemp{\xistr(\hat{W})})
    \end{aligned}
        \right\}
\end{align*}

>>>>

\declaretheorem[numbered=yes,name=Lemma,qed=$\blacksquare$]{lemma}
\declaretheorem[numbered=yes,name=Theorem,qed=$\blacksquare$]{theorem}
\declaretheorem[numbered=yes,name=Definition,qed=$\blacksquare$]{definition}
\declaretheorem[numbered=yes,name=Specification,qed=$\blacksquare$]{specification}

@@

% World operations
\newcommand{\future}{\mathbin{\sqsupseteq}}
\newcommand{\pub}{\var{pub}}
\newcommand{\priv}{\var{priv}}
\newcommand{\futurewk}{\mathbin{\sqsupseteq}^{\var{pub}}}
\newcommand{\futurestr}{\mathbin{\sqsupseteq}^{\var{priv}}}
\newcommand{\heapSat}[3][\heap]{#1 :_{#2} #3}
\newcommand{\memSat}[3][n]{\heapSat[#2]{#1}{#3}}
\newcommand{\memSatPar}[4][n]{\heapSat[#2]{#1 , #4}{#3}}

@@

\newcommand{\Rel}{\plaindom{Rel}}
\newcommand{\Rels}{\plaindom{Rels}}
\newcommand{\States}{\plaindom{State}}
\newcommand{\RegionNames}{\plaindom{RegionName}}
\newcommand{\Regions}{\plaindom{Region}}
\newcommand{\Reg}{\plaindom{Reg}}
\newcommand{\Worlds}{\plaindom{World}}
\newcommand{\Wor}{\plaindom{Wor}}
\newcommand{\Worwk}{\Wor_{\futurewk}}
\newcommand{\Worstr}{\Wor_{\futurestr}}
\newcommand{\xiwk}{\xi_{\var{wk}}}
\newcommand{\xistr}{\xi_{\var{str}}}
\newcommand{\StorePred}{\plaindom{MemSegPred}}
\newcommand{\UPred}[1]{\plaindom{UPred}(#1)}
\newcommand{\DCPred}[1]{\plaindom{P}^\downarrow(#1)}

@@

    c_{\var{adv}} & \defeq ((\rwx,\glob),\start_{\adv},\addrend_{\adv},\start_{\adv}+\olf) \\

@@

    c_\link & \defeq ((\readonly,\glob),\link,\link,\link) \\

@@

  \item $\hs_\adv(\start_\adv) = c_\link$ and all other addresses of $\ms_\adv$ contain instructions.

@@

\begin{proof}[Proof of Lemma~\ref{lem:correctness-g1} (using scall)]
  Let $n$ be given and make the assumptions of the lemma. Define
    W = & [0 \mapsto \iota^\sta (\perma,\ms_{g1} \uplus \ms_\flag)]\\
        & [1 \mapsto \iota^\sta (\perma,\ms_\link)]\\
        & [2 \mapsto \iota^\pwl_{\start_\stk, \addrend_\stk}]\\
        & [3 \mapsto \iota^{\nwl,p}_{\start_\adv,\addrend_\adv}]\\
        & [4 \mapsto \iota_{\malloc,0}]
          \ms_\malloc 
  If we can show
    \label{eq:f4:start-conf-in-obs}
        \npair{(\reg_0\update{\pcreg}{c_\adv}\update{r_\stk}{c_\stk}\update{r_1}{c_{g1}},\ms \uplus \ms_\stk)} \in \observations(W)
  then we are done. The termination assumption gives us that part of $m$ satisfies a private future world of $W$. Region 1 is permanent, so
    m(\flag) = 0
  So we need to show \ref{eq:f4:start-conf-in-obs}. 
  To this end use the FTLR to show $\npair{c_\adv} \in \stder(W)$, so show
    \item $\npair{(\start_\adv,\addrend_\adv)} \in \readCond{}(\glob)(W)$\\
      %TODO
    \item $\npair{(\start_\adv,\addrend_\adv)} \in \writeCond{}(\iota^\nwl,\glob)(W)$\\
      %TODO
  in conclusion $\npair{c_\adv} \in \stder(W)$. We get \ref{eq:f4:start-conf-in-obs} if we show the following
    \item $\memSat{\ms \uplus \ms_\stk}{W}$\\
      %TODO
    \item $\npair{\reg_0\update{r_\stk}{c_\stk}\update{r_1}{c_{g1}}} \in \stdrr(W)$\\
        \item $\npair{c_\stk} \in \stdvr(W)$ \\
          % TODO
        \item $\npair{c_{g1}} \in \stdvr(W)$ \\
          Let $n_1 < n$ and $W_1 \futurestr W$ and show
            \npair[n_1]{\updatePcPerm{c_{g1}}} \in \stder(W_1)
          To this end assume $n_2 \leq n_1$, $\memSat[n_2]{\ms_1}{W_1}$, and $\npair[n_2]{\reg_1} \in \stdrr(W_1)$ and show
            \npair[n']{(\reg_1\update{\pcreg}{\updatePcPerm{c_{g1}}},\ms_1} \in \observations(W_1)
          %TODO

@@

        & [3 \mapsto \iota^\pwl_{\start_\stk, \addrend_\stk}]\\ 

@@

  and use the FTLR on $c_\adv$ (possible due to lemma~\ref{lem:nwlp-subset-pwl} and the chosen world). From this, we get

@@

\section{Logical Relation'}
\subsection{Worlds}
Assume a sufficiently large set of states $\States$ that at least contains the states used in this document.
\begin{definition}
  \[
   \Rels = \{\Phi_\pub \times \Phi \in \powerset{\States^2}\times \powerset{\States^2} \mid \Phi_\pub, \phi \text{ is reflexive and transitive and } \Phi_\pub \subseteq \Phi \}
  \]
\end{definition}
\begin{lemma}
There exists $\Worstr$ and $\Worwk$ are preordered \cofes{} and $\xi_{\var{wk}}$ and $\xi_{\var{str}}$ are isomorphisms such that
\begin{align*}
  \xi_{\var{wk}} :   \Worwk \cong \blater (\nats \finparfun (   & \{\revoked\} + \\
                                                                & \{\temp\} \times \States \times \Rels \times (\States \fun (\Worwk \monnefun \UPred{\HeapSegments})) + \\
                                                                & \{\perma\} \times \States \times \Rels \times (\States \fun (\Worstr \monnefun \UPred{\HeapSegments})),\future_{\var{wk}})) \\ \\
  \xi_{\var{str}} :   \Worstr \cong \blater (\nats \finparfun ( & \{\revoked\} + \\
                                                                & \{\temp\} \times \States \times \Rels \times (\States \fun (\Worwk \monnefun \UPred{\HeapSegments})) + \\
                                                                & \{\perma\} \times \States \times \Rels \times (\States \fun (\Worstr \monnefun \UPred{\HeapSegments})),\future_{\var{str}}))
\end{align*}
\end{lemma}

\begin{theorem}
  There exists a \cofe{} $\Wor$ and preorders $\futurestr$ and $\futurewk$ such that $(\Wor,\futurestr)$ and $(\Wor,\futurewk)$ are preordered \cofes{} and there exists an isomorphism $\xi$ such that
  \begin{align*}
    \xi : \Wor \cong \blater (\nats \finparfun ( & \{\revoked\} + \\
                                          & \{\temp\} \times \States \times \Rels \times (\States \fun (\Worwk \monnefun \UPred{\HeapSegments})) + \\
                                          & \{\perma\} \times \States \times \Rels \times (\States \fun (\Worstr \monnefun \UPred{\HeapSegments}))))
  \end{align*}
 and for $W, W' \in \Wor$
 \[
   W \futurestr W' \Leftrightarrow \xi(W) \futurestr \xi(W')
 \]
and
 \[
   W \futurewk W' \Leftrightarrow \xi(W) \futurewk \xi(W')
 \]
\end{theorem}

We now define the regions to be
\begin{align*}
  \Regions = & \{\revoked\} \uplus \\
             & \{\temp\} \times \States \times \Rel \times (\States \fun (\Worwk \monnefun \UPred{\HeapSegments})) \uplus \\
             & \{\perma\} \times \States \times \Rel \times (\States \fun (\Worstr \monnefun \UPred{\HeapSegments}))
\end{align*}
And the worlds are
\[
  \Worlds = \RegionNames \finparfun \Regions
\]
Where $\RegionNames = \nats$.

@@

Standard regions for when writing locally is permitted:
\begin{align*}
  &\iota_{\start,\addrend}^\pwl : \Regions\\
  &\iota_{\start,\addrend}^\pwl \defeq (\temp,1,=,H^\pwl_{\start,\addrend}) \\
  \\
  &H^\pwl : \Addrs^2 \fun \States \fun (\Worwk \monnefun \UPred{\HeapSegments})\\
  &H^\pwl_{\start,\addrend}\; s \; \hat{W} \defeq \left\{\npair{\hs} \middle|
    \begin{aligned}
      &\dom(\hs) = [\start,\addrend] \land \\
      &\forall \addr \in [\start,\addrend] \ldotp \npair[n-1]{\hs(\addr)} \in \stdvr(\xi(\hat{W}))
    \end{aligned}
        \right\}
\end{align*}
\lau{What is the reason to have the ``view'' always be $\temp$? It seems like it does not play well with the read condition if it is always $\temp$.}
Revoking all temporary regions:
\begin{align*}
  \revokeTemp{} & : \Worlds \fun \Worlds \\
  \revokeTemp{W} & \defeq \lambda r \ldotp 
                   \begin{cases}
                     \revoked            & \text{if }W(r) = (\temp,s,\phi,H) \\
                     W(r)                & \text{otherwise}
                   \end{cases}
\end{align*}
\newcommand{\wrev}[1]{\revokeTemp{#1}}

Standard regions for when write local is not allowed:
\begin{align*}
  &\iota_{\start,\addrend}^{\nwl} : \Regions \\
  &\iota_{\start,\addrend}^{\nwl} \defeq (\temp,1,=,H^\nwl_{start,\addrend}) \\
  \\
  &\iota_{\start,\addrend}^{\nwl,p} : \Regions \\
  &\iota_{\start,\addrend}^{\nwl,p} \defeq (\perma,1,=,H^\nwl_{start,\addrend})\\
  \\
  &H^\nwl : \Addrs^2 \fun \States \fun (\Worstr \monnefun \UPred{\HeapSegments})\\
  &H^\nwl_{\start,\addrend} \; s \;\hat{W} \defeq \left\{\npair{\hs} \middle|
    \begin{aligned}
      &\dom(\hs) = [\start,\addrend] \land \\
      &\forall \addr \in [\start,\addrend] \ldotp \\
      &\quad \npair[n-1]{\hs(\addr)} \in \stdvr(\revokeTemp{\xi(\hat{W})})
    \end{aligned}
        \right\}
\end{align*}
